\section{Introduction to Julia}

\begin{frame}[plain]
\begin{center}
\Huge{(Short) Introduction to Julia}
\end{center}
\end{frame}

%---------------------
\begin{frame}[fragile]
\frametitle{Julia installation}

I am assuming familiarity with command line.

Download Julia the current stable of Julia at
{\scriptsize\url{https://julialang.org/downloads}}
for your operating system.

Unpack the tarball. Usually after unpacking the tarball you should see a new directory
created: \txtinline{julia-1.x.x}, where \txtinline{1.x.x} is the version of Julia.

\begin{textcode}
julia-1.x.x/
├── bin
├── etc
├── include
├── lib
├── libexec
├── LICENSE.md
└── share
\end{textcode}

\end{frame}


%---------------------
\begin{frame}[fragile]
\frametitle{Julia installation (cont'd)}

The Julia binary resides within the \txtinline{bin} directory. You can launch Julia interpreter
by executing the \txtinline{bin/julia} executable. After executing the binary you can see the
the following output:
\begin{textcode}
                _
    _       _ _(_)_     |  Documentation: https://docs.julialang.org
   (_)     | (_) (_)    |
    _ _   _| |_  __ _   |  Type "?" for help, "]?" for Pkg help.
   | | | | | | |/ _` |  |
   | | |_| | | | (_| |  |  Version 1.3.1 (2019-12-30)
  _/ |\__'_|_|_|\__'_|  |  Official https://julialang.org/ release
 |__/                   |
 
 julia>
\end{textcode}

\end{frame}


%---------------------
\begin{frame}[fragile]
\frametitle{Install prerequisites}

\txtinline{PWDFT.jl} depends on several external packages:
\begin{itemize}
\item \txtinline{FFTW.jl}: used for Fast Fourier Transform (FFT).
\item \txtinline{SpecialFunctions}: used for evaluating special functions. For the moment
  this is used for evaluating error function.
\item \txtinline{LibSymspg.jl}: used for finding crystal symmetry and reducing k-points.
  This package is a Julia wrapper for \txtinline{spglib}
  {\scriptsize\url{https://github.com/atztogo/spglib}}.
\item \txtinline{Libxc.jl}: used for evaluating exchange-correlation energy and potential.
  This package is a Julia wrapper for Libxc {\scriptsize\url{https://gitlab.com/libxc/libxc}}.
\end{itemize}

The above packages can be installed by typing the following code in the Julia console.
You also need a working internet connection.
\begin{juliacode}
using Pkg
Pkg.add("FFTW")
Pkg.add("SpecialFunctions")
Pkg.add("LibSymspg")
Pkg.add("Libxc")
\end{juliacode}

\end{frame}



%---------------------
\begin{frame}[fragile]
\frametitle{Install PWDFT.jl}

PWDFT.jl is not yet a registered package so we need to use different command
to install it.
\begin{juliacode}
Pkg.add(PackageSpec(url="https://github.com/f-fathurrahman/PWDFT.jl"))
\end{juliacode}

Import the package by using:
\begin{juliacode}
using PWDFT
\end{juliacode}

It there is no error then we are ready to do some DFT calculations using
\txtinline{PWDFT.jl}.

\end{frame}


\begin{frame}[fragile]
\frametitle{Using Julia interactively}

Operators:

Variables:

Datatype:

Arrays:

Mathematical functions:

Functions:

LinearAlgebra:

\end{frame}
